% !TEX root = ../thesis-example.tex
%
\pdfbookmark[0]{Acknowledgement}{Acknowledgement}
\chapter*{Acknowledgement}
\label{sec:acknowledgement}
\vspace*{-10mm}

I would like to use this opportunity to thank my primary supervisor Alexander Wiebel. Thank you for the thorough review of my work, the published papers we wrote together and the always prolific discussions. Thank you for always believing and having confidence in me, which consequently made me grow as a scientist, teacher, and human. Furthermore, I would like to thank the UX-Vis research group. It is so precious to have a place with peers facing similar hurdles to share news and exchange ideas. Additionally, I am very thankful for all the scientists working with the ZTT. You always made me feel at home, aside from any institutional affiliation.

I would also like to thank Gerik Scheuermann. Your direction, assessment, and support on the papers raised the quality of my work significantly. In addition, the BSV research group was always welcoming and supporting during my visits in Leipzig.

Special thanks belong to my dearest Anna-Lena. Overcoming each hardship and celebrating every small victory was all the sweeter with you. Lastly, I would like to thank my parents. Your endless love and support throughout my life paved the way for my personal well-being, education, and self-fulfilment. However, one of your instructional efforts failed: After all, I did spend a lot of time at the computer.

\begin{itemize}
    \item paper reviewers
    \item spellchecking
\end{itemize}
